---
title: "Barefoot Ocean Guidebook"
author: Katie McCabe
subtitle: "One stop shop for all things BFO"
format: 
  html:
    toc: true
    toc-depth: 3
    code-fold: true
echo: false
output: "asis"
warning: false
include: false
---

#Look into including reference-doc: in yaml for styling

```{r}

# install.packages("shiny.i18n")
library(shiny.i18n)

```

## Mental Models

This is an experimental Quarto document to check whether we can use {shiny.i18n} with Quarto. The idea is simply to create a mock document and try using the package.

[source](https://www.mentalmodelsbox.com/explore)



```{r}

#i18n <- Translator$new(translation_json_path = "data/translations.json")

# file with translations
i18n <- Translator$new(translation_csvs_path = "data")

# csv files for translation
#i18n <- Translator$new(translation_csvs_path = "data/translations/")


# Setting language to "pl" or Polish
# This should be defined in the file passed for 'translation_json_path'

i18n$set_translation_language("pl")

i18n

```

Let's use Inline Code with the format `"r { code here }"`

## `r { i18n$t("test") }`

## `r { i18n$t("report_title") }`

`r { i18n$t("title_desc") }`

`r { i18n$t("source_link") }`

### `r { i18n$t("subhead_one") }`

`r { i18n$t("one_liner") }`

#### `r { i18n$t("subhead_two") }`

`r { i18n$t("definition") }`

#### `r { i18n$t("subhead_three") }`

-   `r { i18n$t("example_one") }`
-   `r { i18n$t("example_two") }`
